High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-01-18 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars and predicts the presence of an inner ring at $\sim$5\,au made mainly of small dust grains.

>>>>

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au made mainly of small dust grains.
